---
title: "mocaredd - package creation steps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{app-generation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(mocaredd)
```



This page shows the different steps to create the package and the main function which is a shiny app, as well as how the app is loaded to shinyapp.io.

Main source for info:

- https://r-pkgs.org/
- https://rtask.thinkr.fr/building-a-shiny-app-as-a-package/
- https://mastering-shiny.org/scaling-packaging.html


## Inital setup:

1. Create a Github repository.
1. Create a R project from Github (See https://happygitwithr.com/ on linking Github repos to Rstudio).
1. Create a package structure inside he project: 
    - `usethis::create_package("PATH/mocaredd")` with PATH the path to the project folder set during the project creation.
1. Add vignettes and pkgdown setup:
    - `usethis::use_pkgdown()`
    - `usethis::use_vignette("app-generation", title = "MCredd - package creation steps")`
1. Add tests architecture:
    - `usethis::use_testthat()` 
1. Add license:
    - `usethis::use_mit_license()` 

## Barebone app

Add dependencies to DESCRIPTION:

- Analysis 

```{r}
usethis::use_package("magrittr")
usethis::use_package("readr")
usethis::use_package("tidyselect")
usethis::use_package("dplyr")
usethis::use_package("ggplot2")
#usethis::use_package("tibble")
#usethis::use_package("forcats")
usethis::use_package("purrr")
usethis::use_package("stringr")
usethis::use_package("rlang")
# usethis::use_package("tidyverse", type = "depends")
usethis::use_package("readxl")
```

- Shiny related

```{r}
usethis::use_package("shiny")
usethis::use_package("shinyjs")
usethis::use_package("shinyWidgets")
usethis::use_package("bslib")
```

- Geospatial

```{r}
usethis::use_package("sf")
usethis::use_package("terra")
usethis::use_package("units")
```


## Run all the time:

```{r}
devtools::document()
devtools::load_all()
shiny_run_mocaredd()

devtools::install()
library(mocaredd)
shiny_run_mocaredd()
```

## Checks


```{r}
devtools::check()

## Run one time 
# usethis::use_testthat()

usethis::use_r("fct_check_data")
usethis::use_test("fct_check_data")
usethis::use_test("fct_combine_mcs_P")
```

