---
title: "MCredd - package creation steps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{app-generation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(MCredd)
```



This page shows the different steps to create the package and the main function which is a shiny app, as well as how the app is loaded to shinyapp.io.

Main source for info:

- https://r-pkgs.org/
- https://rtask.thinkr.fr/building-a-shiny-app-as-a-package/
- https://mastering-shiny.org/scaling-packaging.html


## Inital setup:

1. Create a Github repository.
1. Create a R project from Github (See https://happygitwithr.com/ on linking Github repos to Rstudio).
1. Create a package structure inside he project: 
    - `usethis::create_package("PATH/MCredd")` with PATH the path to the project folder set during the project creation.
1. Add vignettes and pkgdown setup:
    - `usethis::use_pkgdown()`
    - `usethis::use_vignette("app-generation", "MCredd - package creation steps")`



